---
title: "Explore Exploit Analyses"
date: "7/31/22"
output: 
    html_document:
        df_print: 'paged'
        toc: true
        toc_float:
            collapsed: false
            smooth_scroll: true
        number_sections: false
        code_download: true
        self_contained: true
---

```{r dir, include=FALSE}
# Settings
root <- rprojroot::find_rstudio_root_file()
dataDir <- file.path(root, 'data')
codeDir <- file.path(root, 'analysis_code')
figDir <- file.path(root, 'figures')

#default options for code chunks
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = T)
knitr::opts_chunk$set(dpi=600)
```

```{r libraries}
library(afex)
library(tidyverse)
library(sjPlot)
library(knitr)
library(kableExtra)
library(pander)
library(zoo)
```

```{r define functions}
#scale function (z score)
scale_this <- function(x){
  (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE)
}

#standard error
se <- function(x, ...) sqrt(var(x, ..., na.rm=T)/length(x))
```

```{r plot colors and theme}
## Define colors
color1 = "#fe4a49"
color2 = "#2ab7ca"
color3 = "#fed766"
color4 = "#e6e6ea"
color5 = "#f4f4f8"

## Explo plotting theme
explo.theme <- theme(panel.background = element_rect(fill='transparent'),
                    axis.line = element_line(color='black'),
                    panel.grid.minor = element_line(color='transparent'),
                    axis.title.x = element_text(size=16, vjust=-.25),
                    axis.title.y = element_text(size=16, vjust=1),
                    axis.text.x = element_text(size=12, colour="black"),
                    axis.text.y = element_text(size=12, colour="black"),
                    legend.text=element_text(size=12),
                    legend.title = element_text(size = 14),
                    plot.title = element_text(size=16, face = "bold", hjust = .5), 
                    strip.text.x = element_text(size=12), 
                    strip.text.y = element_text(size=12, face="bold"), 
                    strip.background = element_rect(colour= "black", fill = "transparent"))
```

```{r import data}
## Import data
exploData <- read_csv(file.path(dataDir, "explo_choice_data.csv"))
demographicData <- read_csv(file.path(dataDir, "explo_demographics.csv"))
```

```{r merge data}
## merge choice data with demographics
exploAll <- inner_join(exploData, demographicData, by = c("subID"))
```

```{r create age group variables}
# Note: 
# ageGroup3 = children, adolescents, adults
# ageGroup4 = children, adolescents, young adults, adults

#create age group variable in each data frame
demographicData <- demographicData %>% 
   mutate(ageGroup4 = case_when(age < 13 ~ "Children",
                                       age > 12 & age < 18 ~ "Adolescents",
                                       age > 18 & age < 23 ~ "Young Adults",
                                       age > 23 ~ "Adults"),
          ageGroup3 = case_when(age < 13 ~ "Children",
                                       age > 12 & age < 18 ~ "Adolescents",
                                       age > 18 ~"Adults"))

exploAll <- exploAll %>% 
    mutate(ageGroup4 = case_when(age < 13 ~ "Children",
                                       age > 12 & age < 18 ~ "Adolescents",
                                       age > 18 & age < 23 ~ "Young Adults",
                                       age > 23 ~ "Adults"),
           ageGroup3 = case_when(age < 13 ~ "Children",
                                       age > 12 & age < 18 ~ "Adolescents",
                                       age > 18 ~"Adults"))

#reorder levels of age group factors
exploAll$ageGroup3 <- factor(exploAll$ageGroup3, levels = c("Children", "Adolescents", "Adults"))
demographicData$ageGroup3 <- factor(demographicData$ageGroup3, levels = c("Children", "Adolescents", "Adults"))

exploAll$ageGroup4 <- factor(exploAll$ageGroup4, levels = c("Children", "Adolescents", "Young Adults", "Adults"))
demographicData$ageGroup4 <- factor(demographicData$ageGroup4, levels = c("Children", "Adolescents", "Young Adults", "Adults"))
```

# Demographics
## Age and sex distribution
```{r plot age and sex distribution}
ageSexPlot <- ggplot(demographicData, aes(x = trunc(age), fill=sex), color = "black") + 
    geom_histogram(binwidth=1, color = "black") + 
    theme(text=element_text(size=18)) +
    scale_fill_manual(values=c(color1, color2, color3), labels = c("Female", "Male", "Non-binary"), name = "Sex") +
    scale_x_continuous(breaks = seq(from=min(trunc(demographicData$age)), to=max(trunc(demographicData$age)), by=1)) +
    scale_y_continuous(breaks = 0:6) +
    xlab("Age") +
    ylab("Number of Participants") +
    explo.theme
ageSexPlot
```

```{r make demographics tables}
demTable <- demographicData %>% 
    count(sex, ageGroup3) %>% 
    tidyr::spread(key = sex, value=n) %>% 
    mutate(NB = replace_na(NB, 0),
           Total= F+M +NB)
pander(demTable)

demTable2 <- demographicData %>% 
    count(sex, ageGroup4) %>% 
    tidyr::spread(key = sex, value=n) %>% 
    mutate(NB = replace_na(NB, 0),
           Total= F+M +NB)
pander(demTable2)
```

```{r demographic stats}
ageStats <- demographicData %>% 
    group_by(ageGroup3) %>% 
    summarize(
        min_age = min(age),
        max_age = max(age),
        mean_age = mean(age),
        sd_age = sd(age))
pander(ageStats)

ageStats2 <- demographicData %>% 
    group_by(ageGroup4) %>% 
    summarize(
        min_age = min(age),
        max_age = max(age),
        mean_age = mean(age),
        sd_age = sd(age))
pander(ageStats2)
```

## Relation between age and IQ
```{r model age IQ correlation}
#select relevant variables
demographicData.filtered <- demographicData %>%
    select(c(age, IQ)) %>%
    drop_na()

#scale
demographicData.filtered$ageScaled <- scale_this(demographicData.filtered$age)
demographicData.filtered$IQScaled <- scale_this(demographicData.filtered$IQ)


age.IQ.lm <- lm(IQScaled ~ ageScaled, data = demographicData.filtered)
pander(age.IQ.lm)
```

```{r plot age and IQ}
age_IQ_plot <- ggplot(demographicData.filtered, aes(x = age, y = IQ)) +
    geom_point(color = color1) +
    geom_smooth(method = "lm", color = color2, fill = color2) +
    xlab("Age") +
    ylab("WASI Score (Full-Scale IQ)") +
    explo.theme
age_IQ_plot
```

### IQ scores across age groups
```{r mean IQ by age group}
meanIQ <- demographicData %>%
    group_by(ageGroup3) %>%
    summarize(N = n(),
              meanMR = mean(WASI_mrT, na.rm = T),
              meanVerbal= mean(WASI_verbalT, na.rm = T),
              meanIQ = mean(IQ, na.rm = T),
              sdIQ = sd(IQ, na.rm = T))
pander(meanIQ)

meanIQ2 <- demographicData %>%
    group_by(ageGroup4) %>%
    summarize(N = n(), 
              meanMR = mean(WASI_mrT, na.rm = T),
              meanVerbal= mean(WASI_verbalT, na.rm = T),
              meanIQ = mean(IQ, na.rm = T),
              sdIQ = sd(IQ, na.rm = T))
pander(meanIQ2)
```


# Task statistics
```{r block information}
#label blocks as hard or easy
blockInfo <- read_csv(file.path(dataDir, "explo_block_difficulty.csv"))
exploAll <- full_join(exploAll, blockInfo, by = c("subID", "blockID")) %>%
    mutate(blockDifficulty = case_when(blockDifficulty == 0 ~ 'Easy',
                                       blockDifficulty == 1 ~ 'Hard'))
```

## Average number of times each hiding spot was encountered
```{r number of times each spot encountered}
#First, label all the novel hiding spots in each block
novelStim <- exploAll %>%
    select(subID, blockID, trialID, trialStimID_1, trialStimID_2, exposureHistory_t_1, exposureHistory_t_2) %>%
    pivot_longer(cols = c(trialStimID_1, trialStimID_2), names_to = "stimSide", names_prefix = "trialStimID_", values_to = "stim") %>%
    pivot_longer(cols = c(exposureHistory_t_1, exposureHistory_t_2), names_to = "stimSide2", names_prefix = "exposureHistory_t_", values_to = "exposeHist") %>%
    filter(stimSide == stimSide2) %>%
    select(-stimSide2) %>%
    filter(blockID > 1) %>%
    filter(exposeHist == 0) %>%
    select(subID, blockID, stim) %>%
    mutate(novel = 1)
    
#Compute the mean exposure history for novel and non-novel options in each block
exposeHist <- exploAll %>%
    select(subID, blockID, trialID, trialStimID_1, trialStimID_2, exposureHistory_t_1, exposureHistory_t_2) %>%
    pivot_longer(cols = c(trialStimID_1, trialStimID_2), names_to = "stimSide", names_prefix = "trialStimID_", values_to = "stim") %>%
    pivot_longer(cols = c(exposureHistory_t_1, exposureHistory_t_2), names_to = "stimSide2", names_prefix = "exposureHistory_t_", values_to = "exposeHist") %>%
    filter(stimSide == stimSide2) %>%
    select(-stimSide2) %>%
    filter(blockID > 1) 

exposeHist <- full_join(exposeHist, novelStim, by = c("subID", "blockID", "stim")) %>%
    group_by(trialID, novel) %>%
    summarize(meanExposeHist = mean(exposeHist),
              sdExposeHist = sd(exposeHist),
              maxExposeHist = max(exposeHist),
              minExposeHist = min(exposeHist))

pander(exposeHist)
```


# Choice behavior

## How many reaction times were under 200 ms?
```{r filter RT}

#save unfiltered data
exploAllUnfiltered <- exploAll

#determine how many RTs < 200 ms
fastRTs <- exploAllUnfiltered %>%
    filter(RT < .2) %>%
    filter(!is.na(selectedStimID)) %>%
    group_by(subID) %>%
    summarize(n_fastRTs = n())

total_fast_RTs <- sum(fastRTs$n_fastRTs)
total_fast_RTs

#69 fast RTs

normalRTs <- exploAllUnfiltered %>%
    filter(RT > .2) %>%
    filter(!is.na(selectedStimID)) %>%
    group_by(subID) %>%
    summarize(n_normalRTs = n())

total_normal_RTs <- sum(normalRTs$n_normalRTs)
total_normal_RTs
#18146 normal RTs

#exclude fast RT trials from exploAll
exploAll <- exploAll %>%
    filter(!is.na(selectedStimID)) %>%
    filter(RT > .2)
```

## Model: relation between age, block difficulty, and reward earned
```{r reward earned age model}
#compute reward earned
reward_earned <- exploAll %>%
    group_by(subID, age, IQ, blockDifficulty) %>%
    summarize(total_reward = sum(reward, na.rm = T))

#filter data
reward_earned.filtered <- reward_earned %>%
    select(total_reward, age, blockDifficulty) %>%
    drop_na()

#scale age and reward
reward_earned.filtered$ageScaled <- scale_this(reward_earned.filtered$age)
reward_earned.filtered$rewardScaled <- scale_this(reward_earned.filtered$total_reward)

#set sum contrasts
options(contrasts = rep("contr.sum", 2))

#run model
reward.age.blockDiff.lm <- lm(rewardScaled ~ ageScaled * blockDifficulty, data = reward_earned.filtered)
pander(summary(reward.age.blockDiff.lm))
# main effect of age
# no effect of block difficulty
# no age x difficulty interaction effect
```

## Model: relation between age, block difficulty, IQ, and reward earned
```{r reward earned age model with IQ}
#filter IQ
reward_earned_IQ <- reward_earned %>%
    select(IQ, age, total_reward, blockDifficulty) %>%
    drop_na()

#scale variables
reward_earned_IQ$ageScaled <- scale_this(reward_earned_IQ$age)
reward_earned_IQ$reward_scaled <- scale_this(reward_earned_IQ$total_reward)
reward_earned_IQ$IQScaled <- scale_this(reward_earned_IQ$IQ)

reward.age.IQ.lm <- lm(reward_scaled ~ ageScaled * IQScaled * blockDifficulty, data = reward_earned_IQ) 

#show results
pander(reward.age.IQ.lm)
# main effect of age
# main effect of IQ
# no other sig. effects / interactions
```

## Plot: Reward earned by age
```{r reward earned}
reward_earned_total <- reward_earned %>% 
    group_by(subID, age, blockDifficulty) %>%
    summarize(total_reward = sum(total_reward))

#plot
reward_age_plot <- ggplot(reward_earned_total, aes(x = age, y = total_reward, color = blockDifficulty, fill = blockDifficulty)) +
    geom_point() +
    geom_smooth(method = "lm") + 
    scale_color_manual(values = c(color1, color2), name = "Block Difficulty", labels = c("Easy", "Hard")) +
    scale_fill_manual(values = c(color1, color2), name = "Block Difficulty", labels = c("Easy", "Hard")) +
    xlab("Age") +
    ylab("Total Reward Earned") +
    geom_hline(yintercept = 37.5, linetype = "dashed") +
    explo.theme
reward_age_plot  
```

## Distribution of choices by age group
```{r reward distributions}
#add the high, med, low stim reward numbers to the data frame
reward_dist <- exploAll %>%
    select(subID, blockID, reward_probs_1:reward_probs_12) %>%
    unique() %>%
    pivot_longer(cols = c(reward_probs_1:reward_probs_12), 
                 names_to = "stimNum", 
                 values_to = "winProb",
                 names_prefix = "reward_probs_") %>%
    group_by(subID, blockID) %>%
    filter(winProb > 0) %>%
    mutate(stimRanking = 4-rank(winProb)) 

high_rew_stim <- reward_dist %>%
    filter(stimRanking == 1) %>%
    mutate(highRewStimNum = stimNum,
           highRewWinProb = winProb) %>%
    select(-c(stimNum, winProb, stimRanking))

med_rew_stim <- reward_dist %>%
    filter(stimRanking == 2) %>%
    mutate(medRewStimNum = stimNum,
           medRewWinProb = winProb) %>%
    select(-c(stimNum, winProb, stimRanking))

low_rew_stim <- reward_dist %>%
    filter(stimRanking == 3) %>%
    mutate(lowRewStimNum = stimNum,
           lowRewWinProb = winProb) %>%
    select(-c(stimNum, winProb, stimRanking))

stimRewardInfo <- high_rew_stim %>%
    full_join(med_rew_stim, by = c("subID", "blockID")) %>%
    full_join(low_rew_stim, by = c("subID", "blockID"))
```

```{r determine selected stim}
processedData <- exploAll %>%
    select(subID, blockID, trialID, selectedStimID, rejectedStimID, RT, reward, numBlockStims) %>%
    mutate(selectedStimID = as.numeric(selectedStimID),
           rejectedStimID = as.numeric(rejectedStimID))

processedData <- processedData %>%
    full_join(stimRewardInfo, by = c("subID", "blockID")) %>%
    full_join(novelStim, by = c("subID", "blockID")) %>%
    rename(novelStimNum = stim) %>%
    select(-novel)
```

## Plot: Choice type by age group
```{r choice type data processing}
choice_type <- processedData %>%
    mutate(reward_chosen = case_when(selectedStimID == highRewStimNum ~ "high",
                                     selectedStimID == medRewStimNum ~ "med",
                                     selectedStimID == lowRewStimNum ~ "low"),
           reward_rejected =  case_when(rejectedStimID == highRewStimNum ~ "high",
                                     rejectedStimID == medRewStimNum ~ "med",
                                     rejectedStimID == lowRewStimNum ~ "low"),
           novel_chosen = case_when(selectedStimID == novelStimNum ~ 1,
                                     selectedStimID != novelStimNum ~ 0))

# get sub demographic info
ageData <- demographicData %>%
    select(subID, age, ageGroup3, ageGroup4, IQ)

#add age group
choice_type <- full_join(choice_type, ageData, by = c("subID"))
choice_type$reward_chosen <- factor(choice_type$reward_chosen, levels = c("low", "med", "high"))

#compute counts
rewardSubCounts <- choice_type %>%
    group_by(subID, age, ageGroup3, reward_chosen) %>%
    drop_na() %>%
    summarize(N = n()) %>%
    ungroup() %>%
    group_by(subID) %>%
    mutate(prop = N / sum(N))

rewardCounts <- rewardSubCounts %>%
    group_by(ageGroup3, reward_chosen) %>%
    summarize(meanProp = mean(prop, na.rm = T),
              seProp = se(prop))

#plot
choiceCountsPlot <- ggplot(rewardCounts, aes(x = reward_chosen, fill = ageGroup3, y = meanProp)) +
    geom_bar(stat = "identity", position = "dodge", color = "black") +
    geom_errorbar(width = .1, position = position_dodge(width = .9), aes(ymin = meanProp - seProp, ymax = meanProp + seProp)) +
    scale_fill_manual(values = c(color1, color2, color3, color4), name = "Age Group") +
    scale_x_discrete(labels = c("Low", "Medium", "High")) +
    xlab("Value of Selected Option") +
    ylab("Proportion of Choices") +
    theme_classic()
choiceCountsPlot
```

## Model: Optimal choices by age and block difficulty
```{r optimal choices by age and block difficulty}
#determine whether the participant made the optimal choice on each trial
opt_choices <- choice_type %>%
    mutate(opt_choice = case_when(reward_chosen == "high" ~ 1,
                     reward_chosen == "med" & reward_rejected == "low" ~ 1,
                     reward_chosen == "med" & reward_rejected == "high" ~ 0,
                     reward_chosen == "low" ~ 0)) %>%
    full_join(blockInfo, by = c("subID", "blockID")) %>%
    mutate(blockDifficulty = factor(blockDifficulty)) %>%
    drop_na()

#select variables and filter
opt_choices.filtered <- opt_choices %>%
    select(opt_choice, age, blockDifficulty, trialID, subID) %>%
    drop_na()

#scale variables
opt_choices.filtered$ageScaled <- scale_this(opt_choices.filtered$age)
opt_choices.filtered$trialScaled <- scale_this(opt_choices.filtered$trialID)


optChoice.age.model <- mixed(opt_choice ~ ageScaled * blockDifficulty * trialScaled + 
                                 (blockDifficulty + trialScaled | subID), 
                             data = opt_choices.filtered,
                             family = "binomial",
                             method = "LRT",
                             control = glmerControl(optimizer = "bobyqa"),
                             expand_re = T)
                            
#show results
optChoice.age.model

#Note: singular fit w/ interaction in RE

#main effect of age
#main effect of block difficulty
#main effect of trial 
```

## Model: Optimal choices by age, IQ and block difficulty
```{r optimal choices by age, IQ, and block difficulty}
#remove participants w/o IQ scores
opt_choices_IQ <- opt_choices %>%
    filter(IQ > 0)

#select variables and filter
opt_choices_IQ.filtered <- opt_choices_IQ %>%
    select(opt_choice, age, blockDifficulty, trialID, IQ, subID) %>%
    drop_na()

#rescale variables
opt_choices_IQ.filtered$trialScaled <- scale_this(opt_choices_IQ.filtered$trialID)
opt_choices_IQ.filtered$ageScaled <- scale_this(opt_choices_IQ.filtered$age)
opt_choices_IQ.filtered$IQScaled <- scale_this(opt_choices_IQ.filtered$IQ)


optChoice.age.IQ.model <- mixed(opt_choice ~ ageScaled * blockDifficulty * trialScaled * IQScaled + 
                                 (blockDifficulty + trialScaled | subID), 
                             data = opt_choices_IQ.filtered,
                             family = "binomial",
                             method = "LRT",
                             control = glmerControl(optimizer = "bobyqa"),
                             expand_re = T)
                            

#show results
optChoice.age.IQ.model

# main effect of age
# main effect of block difficulty
# main effect of trial
```

## Plot: Optimal choices by age and block difficulty
```{r opt choice age plot}
mean_opt_choice <- opt_choices %>%
    group_by(subID, age, blockDifficulty) %>%
    summarize(meanOptChoice = mean(opt_choice, na.rm = T))

opt_choice_plot <- ggplot(mean_opt_choice, aes(x = age, y = meanOptChoice, color = blockDifficulty, fill = blockDifficulty)) +
    geom_point() +
    geom_smooth(method = "lm") + 
    scale_color_manual(values = c(color1, color2), name = "Block Difficulty", labels = c("Easy", "Hard")) +
    scale_fill_manual(values = c(color1, color2), name = "Block Difficulty", labels = c("Easy", "Hard")) +
    xlab("Age") +
    ylab("Proportion of Optimal Choices") +
    geom_hline(yintercept = .5, linetype = "dashed") +
    explo.theme
opt_choice_plot
```

## Plot: RT distributions
```{r plot RT distributions}
hist(exploAll$RT)

exploAll$logRT <- log(exploAll$RT)
hist(exploAll$logRT)
```

## Model: RTs by age
```{r RT age model}

#select variables and filter
exploAll.filtered <- exploAll %>%
    select(logRT, age, blockDifficulty, subID) %>%
    drop_na()

exploAll.filtered$ageScaled <- scale_this(exploAll.filtered$age)

#run model
RT.age.model <- mixed(logRT ~ ageScaled * blockDifficulty + 
                                 (blockDifficulty | subID), 
                             data = exploAll.filtered,
                             method = "S",
                             control = lmerControl(optimizer = "bobyqa"),
                             expand_re = T)
RT.age.model 

#main effect of block difficulty
```

```{r RT age IQ model}
exploAll_IQ <- exploAll %>%
    filter(IQ > 0)

#select variables and filter
exploAll_IQ.filtered <- exploAll_IQ %>%
    select(logRT, age, blockDifficulty, IQ, subID) %>%
    drop_na()

exploAll_IQ.filtered$ageScaled <- scale_this(exploAll_IQ.filtered$age)
exploAll_IQ.filtered$IQScaled <- scale_this(exploAll_IQ.filtered$IQ)



RT.age.IQ.model <- mixed(logRT ~ ageScaled * blockDifficulty *IQScaled + 
                                 (blockDifficulty | subID), 
                             data = exploAll_IQ.filtered,
                             method = "S",
                             control = lmerControl(optimizer = "bobyqa"),
                             expand_re = T)
RT.age.IQ.model 
# main effect of age
# main effect of block difficulty
# main effect of IQ
# marginal age x block difficulty x IQ interaction
```

## Plot: Mean RT by age
```{r RTs}
mean_RTs <- exploAll %>%
    group_by(subID, age) %>%
    summarize(mean_RT = mean(RT, na.rm = T))

#plot
RT_age_plot <- ggplot(mean_RTs, aes(x = age, y = mean_RT)) +
    geom_point(color = color1) +
    geom_smooth(method = "lm", color = color2, fill = color2) +
    xlab("Age") +
    ylab("Mean Reaction Time (seconds)") +
    explo.theme
RT_age_plot  
```


# Influence of choice features across age
For the regression analyses, we first compute three learning features for each of the two options presented: expected value, uncertainty, and novelty. The participant's belief about the probability of winning for each option can be described with a beta distribution, where the alpha parameter indicates the number of wins and the beta parameter indicates the number of losses. Because neither of the parameters of the distribution can be zero, we add 1 to the number of previous wins and losses prior to computing any of the learning features.

The expected value for each option is defined as the mean of the beta distribution:
$$\frac{\alpha}{\alpha + \beta}$$

The uncertainty over each option is defined as the variance of the beta distribution:
$$\frac{\alpha * \beta}{(\alpha * \beta)^2 + (\alpha + \beta + 1)}$$

The novelty of each option is determined by taking the variance of a different beta distribution, where the alpha parameter reflects the exposure history (number of trials on which option was presented) and the beta parameter is 1. As alpha increases, the variance will decrease. 

In the regression models, we include the *difference* in these feature values between the left and right option, and determine how they influence the participant's probability of selecting the left option. In the models, higher features values indicate that relative to the right option, the left option is:
- more valuable
- more uncertain
- more novel

```{r compute learning features}
#Note: 
# Variables post-ended with _1 = left option
# Variables post-ended with _2 = right option

#compute value, uncertainty, and novelty for each trial
data.all <- exploAll
data.all$subID = as.factor(data.all$subID)

# compute expected value and variance of the LEFT option 
betaA = data.all$winHistory_b_1+1 
betaB = data.all$lossHistory_b_1+1
data.all$ev_1 = betaA / (betaA + betaB) #number of wins / number of wins + number of losses
data.all$var_1 = (betaA*betaB)/((betaA+betaB)^2 * (betaA+betaB+1)) #variance
 
# compute expected value of the RIGHT option according to a beta distribution
betaA = data.all$winHistory_b_2+1
betaB = data.all$lossHistory_b_2+1
data.all$ev_2 = betaA / (betaA + betaB)
data.all$var_2 = (betaA*betaB)/((betaA+betaB)^2 * (betaA+betaB+1))

#compute EV of the left and right option assuming values do not reset
betaA = data.all$winHistory_t_1 + 1
betaB = data.all$lossHistory_t_1 + 1
data.all$ev_1_noReset = betaA / (betaA + betaB)
betaA = data.all$winHistory_t_2 + 1
betaB = data.all$lossHistory_t_2 + 1
data.all$ev_2_noReset = betaA / (betaA + betaB)
  
# feed exposure in as alpha in a beta distribution to compute novelty on the same scale as uncertainty
betaA = data.all$exposureHistory_t_1+1
betaB = 1
data.all$novel_1 = (betaA*betaB)/( (betaA+betaB)^2 * (betaA+betaB+1)) #get variance in exposure
  
# for the RIGHT option
betaA = data.all$exposureHistory_t_2+1
betaB = 1
data.all$novel_2 = (betaA*betaB)/((betaA+betaB)^2 * (betaA+betaB+1)) #with repeated exposure, variance of beta distribution will decrease
```

```{r select features for regression}
# probe predictors of choice (left vs right)
data.model <- data.all %>%
    filter(!is.na(selectedStimID)) %>% #exclude trials where they did not make a choice
    select(subID, 
          trialID, 
          blockID,
          numBlockStims, 
          trialStimID_1, 
          trialStimID_2, 
          selectedStimID, 
          ev_1, 
          ev_2, 
          ev_1_noReset,
          ev_2_noReset,
          var_1, 
          var_2, 
          novel_1, 
          novel_2, 
          age,
          ageGroup3,
          ageGroup4, 
          IQ,
          RT)
    
# compute difference in left - right option feature values 
data.model$evDiff = data.model$ev_1 - data.model$ev_2
data.model$varDiff = data.model$var_1 - data.model$var_2
data.model$novelDiff = data.model$novel_1 - data.model$novel_2
data.model$evDiff_noReset = data.model$ev_1_noReset - data.model$ev_2_noReset

# compute difference in more uncertain vs. less uncertain expected values
# compute difference in more novel vs. more familiar expected values
data.model <- data.model %>%
    mutate(evUncertainDiff = case_when(var_1 > var_2 ~ ev_1 - ev_2,
                                       var_1 < var_2 ~ ev_2 - ev_1),
           evNovelDiff = case_when(novel_1 > novel_2 ~ ev_1 - ev_2,
                                   novel_1 < novel_2 ~ ev_2 - ev_1))

# determine which option was selected
data.model <- data.model %>%
    mutate(leftChoice = case_when(selectedStimID == trialStimID_1 ~ 1,
                                  selectedStimID == trialStimID_2 ~ 0),
           uncertainChoice = case_when(var_1 > var_2 & leftChoice == 1 ~ 1,
                                       var_1 > var_2 & leftChoice == 0 ~ 0,
                                       var_1 < var_2 & leftChoice == 1 ~ 0,
                                       var_1 < var_2 & leftChoice == 0 ~ 1),
           novelChoice  = case_when(novel_1 > novel_2 & leftChoice == 1 ~ 1,
                                       novel_1 > novel_2 & leftChoice == 0 ~ 0,
                                       novel_1 < novel_2 & leftChoice == 1 ~ 0,
                                       novel_1 < novel_2 & leftChoice == 0 ~ 1),
           valuableChoice = case_when( ev_1 > ev_2 & leftChoice == 1 ~ 1,
                                       ev_1 > ev_2 & leftChoice == 0 ~ 0,
                                       ev_1 < ev_2 & leftChoice == 1 ~ 0,
                                       ev_1 < ev_2 & leftChoice == 0 ~ 1))


```

```{r compute value, uncertainty, and novelty means}
value_means <- data.model %>%
    mutate(evDiffGroup = cut(evDiff, breaks = c(-1, -.2, -.1, .1, .2, 1))) %>%
    group_by(ageGroup3, evDiffGroup) %>%
    summarize(meanChoice = mean(leftChoice),
              seChoice = se(leftChoice)) %>%
    drop_na() %>%
    mutate(group = "Higher Value")

value_means2 <- data.model %>%
    mutate(evDiffGroup = cut(evDiff, breaks = c(-1, -.2, -.1, .1, .2, 1))) %>%
    group_by(ageGroup4, evDiffGroup) %>%
    summarize(meanChoice = mean(leftChoice),
              seChoice = se(leftChoice)) %>%
    drop_na() %>%
    mutate(group = "Higher Value")

uncertainty_means <- data.model %>%
    mutate(evDiffGroup = cut(evUncertainDiff, breaks = c(-1, -.2, -.1, .1, .2, 1))) %>%
    group_by(ageGroup3, evDiffGroup) %>%
    summarize(meanChoice = mean(uncertainChoice, na.rm = T),
              seChoice = se(uncertainChoice)) %>%
    drop_na() %>%
    mutate(group = "More Uncertain")

uncertainty_means2 <- data.model %>%
    mutate(evDiffGroup = cut(evUncertainDiff, breaks = c(-1, -.2, -.1, .1, .2, 1))) %>%
    group_by(ageGroup4, evDiffGroup) %>%
    summarize(meanChoice = mean(uncertainChoice, na.rm = T),
              seChoice = se(uncertainChoice)) %>%
    drop_na() %>%
    mutate(group = "More Uncertain")

novel_means <- data.model %>%
    mutate(evDiffGroup = cut(evNovelDiff, breaks = c(-1, -.2, -.1, .1, .2, 1))) %>%
    group_by(ageGroup3, evDiffGroup) %>%
    summarize(meanChoice = mean(novelChoice, na.rm = T),
              seChoice = se(novelChoice)) %>%
    drop_na() %>%
    mutate(group = "More Novel")

novel_means2 <- data.model %>%
    mutate(evDiffGroup = cut(evNovelDiff, breaks = c(-1, -.2, -.1, .1, .2, 1))) %>%
    group_by(ageGroup4, evDiffGroup) %>%
    summarize(meanChoice = mean(novelChoice, na.rm = T),
              seChoice = se(novelChoice)) %>%
    drop_na() %>%
    mutate(group = "More Novel")
```

## Plot: Influence of learning features on choice behavior
```{r plot novelty seeking and uncertainty aversion together}
#combine means
feature_means <- rbind(value_means, uncertainty_means, novel_means)

feature_plot <- ggplot(feature_means, aes(x = evDiffGroup, y = meanChoice, color = ageGroup3)) +
    facet_wrap(~group) +
    geom_point(size = 2.5) +
    geom_errorbar(aes(ymin = meanChoice - seChoice, ymax = meanChoice + seChoice), width = 0) +
    scale_color_manual(values = c(color1, color2, color3, color4), name = "Age Group") +
    scale_shape_manual(values = c(1, 2, 3), name = " ") +
    geom_hline(yintercept = .5, linetype = 'dashed') +
    ylab("Proportion Chosen") +
    xlab("Expected Value Difference") +
    explo.theme + 
    theme(panel.border = element_rect(color = "black", fill = NA, size = .5),
          axis.line = element_blank(),
          strip.background = element_rect(fill = NA, colour = "black", size = .5),
          strip.text = element_text(face = "bold"),
          axis.title.x = element_text(vjust=-0.5),
          axis.text.x = element_text(size = 8)) 
feature_plot
```

```{r feature plot with age groups as facets, fig.width=8, fig.height=4}
feature_plot_ageFacets <- ggplot(feature_means, aes(x = evDiffGroup, y = meanChoice, color = group)) +
    facet_wrap(~ageGroup3) +
    geom_point(size = 2) +
    geom_errorbar(aes(ymin = meanChoice - seChoice, ymax = meanChoice + seChoice), width = 0) +
    scale_color_manual(values = c(color3, color1, color2), name = "",
                       labels = c("Left vs. Right",
                              "More vs. Less Novel",
                                  "More vs. Less Uncertain")) +
    geom_hline(yintercept = .5, linetype = 'dashed') +
    ylab("Proportion Chosen") +
    xlab("Expected Value Difference") +
    geom_line(aes(group = group), size = .5, fill = "white") + 
    explo.theme + 
    theme(panel.border = element_rect(color = "black", fill = NA, size = .5),
          axis.line = element_blank(),
          strip.background = element_rect(fill = NA, colour = "black", size = .5),
          strip.text = element_text(face = "bold"),
          axis.title.x = element_text(vjust=-0.5),
          axis.text.x = element_text(size = 8),
          legend.position = "top") 
feature_plot_ageFacets
```


## Plot: Choices on equal expected value trials
```{r proportion of trials more certain and more novel chosen equal EV}
uncertainty_novelty_means_equal_value <- data.model %>%
    mutate(evDiffGroup = cut(evDiff, breaks = c(-.05, .05))) %>%
    group_by(evDiffGroup) %>%
    summarize(meanUncertainChoice = mean(uncertainChoice, na.rm = T),
              seUncertainChoice = se(uncertainChoice),
              meanNovelChoice = mean(novelChoice, na.rm = T),
              seNovelChoice = se(novelChoice)) %>%
    drop_na()
pander(uncertainty_novelty_means_equal_value)

uncertainty_novelty_age_group_means_equal_value <- data.model %>%
    mutate(evDiffGroup = cut(evDiff, breaks = c(-.05, .05))) %>%
    group_by(ageGroup3, evDiffGroup) %>%
    summarize(meanUncertainChoice = mean(uncertainChoice, na.rm = T),
              seUncertainChoice = se(uncertainChoice),
              meanNovelChoice = mean(novelChoice, na.rm = T),
              seNovelChoice = se(novelChoice)) %>%
    drop_na()
pander(uncertainty_novelty_age_group_means_equal_value)

uncertainty_novelty_age_group_means_equal_value2 <- data.model %>%
    mutate(evDiffGroup = cut(evDiff, breaks = c(-.05, .05))) %>%
    group_by(ageGroup4, evDiffGroup) %>%
    summarize(meanUncertainChoice = mean(uncertainChoice, na.rm = T),
              seUncertainChoice = se(uncertainChoice),
              meanNovelChoice = mean(novelChoice, na.rm = T),
              seNovelChoice = se(novelChoice)) %>%
    drop_na()

```

```{r proportion of trials more certain and more novel chosen equal EV continuous age, fig.height=4, fig.width=4}
uncertainty_novelty_sub_means_equal_value <- data.model %>%
    mutate(evDiffGroup = cut(evDiff, breaks = c(-.05, .05))) %>%
    group_by(subID, age, evDiffGroup) %>%
    summarize(meanUncertainChoice = mean(uncertainChoice, na.rm = T),
              meanNovelChoice = mean(novelChoice, na.rm = T)) %>%
    drop_na() %>% 
    pivot_longer(cols = c(meanUncertainChoice, meanNovelChoice),
                 names_to = "feature",
                 values_to = "prop")

 
 feature_cont_age_plot2 <- ggplot(uncertainty_novelty_sub_means_equal_value, 
                                aes(x = age, y = prop, color = feature, fill = feature)) +
    geom_point() +
    geom_smooth(method = "lm") +
    scale_color_manual(values = c(color2, color1), name = "", 
                      labels = c("More Novel",
                                 "More Uncertain")) +
    scale_fill_manual(values = c(color2, color1), name = "", 
                      labels = c("More Novel",
                                 "More Uncertain")) +
    ylab("Proportion Chosen") +
    xlab("Age") +
    explo.theme +
    coord_cartesian(ylim = c(0, 1)) +
    geom_hline(yintercept = .5, linetype = 'dashed') +
    theme(legend.position = "top")
 feature_cont_age_plot2  
```

```{r proportion of trials more certain and more novel chosen equal EV plot, fig.height=4, fig.width=4}
uncertainty_novelty_indiv_means_equal_value <- data.model %>%
    mutate(evDiffGroup = cut(evDiff, breaks = c(-.05, .05))) %>%
    group_by(subID, age, ageGroup3, ageGroup4, evDiffGroup) %>%
    summarize(more_uncertain_choice = mean(uncertainChoice, na.rm = T),
              more_novel_choice = mean(novelChoice, na.rm = T)) %>%
    drop_na() %>%
    pivot_longer(cols = c(more_uncertain_choice, more_novel_choice), 
                 names_to = "feature", 
                 values_to = "meanChoice")

equalEVplot <- ggplot(uncertainty_novelty_indiv_means_equal_value, aes(x = ageGroup3, y = meanChoice, color = feature, fill = feature)) +
    geom_point(position=position_jitterdodge(), aes(color = feature)) +
    geom_boxplot(color = "black", alpha = .3, outlier.color = NA) +
    scale_color_manual(values = c(color1, color2), name = "", 
                      labels = c("More Novel",
                                 "More Uncertain")) +
    scale_fill_manual(values = c(color1, color2), name = "", 
                      labels = c("More Novel",
                                 "More Uncertain")) +
    geom_hline(yintercept = .5, linetype = 'dashed') +
    explo.theme + 
    ylab("Proportion Chosen") +
    xlab("Age Group") +
    theme(legend.position = "top")
equalEVplot
```


## Model: Influence of age, value, uncertainty, and novelty on choice
```{r choice features model: age}

#select variables
data.model.1 <- data.model %>%
    select(c(leftChoice, evDiff, varDiff, novelDiff, age, subID)) %>%
    drop_na()

#scale continuous variables
data.model.1$evDiffScaled = scale_this(data.model.1$evDiff)
data.model.1$varDiffScaled = scale_this(data.model.1$varDiff)
data.model.1$novelDiffScaled = scale_this(data.model.1$novelDiff)
data.model.1$ageScaled <- scale_this(data.model.1$age)

feature.age.model <- mixed(leftChoice ~ 
                               evDiffScaled + 
                               varDiffScaled + 
                               novelDiffScaled +
                               evDiffScaled:ageScaled +
                               varDiffScaled:ageScaled + 
                               novelDiffScaled:ageScaled +
                               (evDiffScaled + varDiffScaled + novelDiffScaled || subID),
                   data.model.1, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T)
feature.age.model 

#note: did not converge w/ correlated random effects
```

```{r plot model effects: age}
plot_model(feature.age.model,
           type = "est",
           show.values = TRUE,
           show.p = TRUE,
           colors = c(color1, color2)) +
     scale_x_discrete(labels =  c(
         "Age x Novelty",
         "Age x Uncertainty",
         "Age x Expected Value",
         "Novelty", 
         "Uncertainty", 
         "Expected Value")) + 
    ggtitle("Predictors of choice") +
    geom_hline(yintercept = 0, color = "grey", linetype = "dashed") +
    explo.theme
```

## Model: Influence of age, IQ, value, uncertainty, and novelty on choice
```{r choice features model: age and IQ}
#filter out participants w/o IQ scores (n = 2)
data.model.IQ <- data.model %>%
    select(c(leftChoice, evDiff, varDiff, novelDiff, age, subID, IQ)) %>%
    drop_na()

#scale continuous variables
data.model.IQ$evDiffScaled <- scale_this(data.model.IQ$evDiff)
data.model.IQ$varDiffScaled <- scale_this(data.model.IQ$varDiff)
data.model.IQ$novelDiffScaled <- scale_this(data.model.IQ$novelDiff)
data.model.IQ$ageScaled <- scale_this(data.model.IQ$age)
data.model.IQ$IQScaled <- scale_this(data.model.IQ$IQ)


feature.age.IQ.model <- mixed(leftChoice ~ 
                               evDiffScaled + 
                               varDiffScaled + 
                               novelDiffScaled +
                               evDiffScaled:ageScaled +
                               varDiffScaled:ageScaled + 
                               novelDiffScaled:ageScaled +
                               evDiffScaled:IQScaled +
                               varDiffScaled:IQScaled + 
                               novelDiffScaled:IQScaled +
                               evDiffScaled:ageScaled:IQScaled +
                               varDiffScaled:ageScaled:IQScaled + 
                               novelDiffScaled:ageScaled:IQScaled +
                               (evDiffScaled + varDiffScaled + novelDiffScaled | subID),
                   data.model.IQ, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T)
feature.age.IQ.model

summary(feature.age.IQ.model)
```

```{r plot model effects: age and IQ}
plot_model(feature.age.IQ.model,
           type = "est",
           show.values = TRUE,
           show.p = TRUE,
           colors = c(color1, color2)) +
     scale_x_discrete(labels =  c(
         "Age x IQ x Novelty",
         "Age x IQ x Uncertainty",
         "Age x IQ x Expected Value",
         "IQ x Novelty",
         "IQ x Uncertainty",
         "IQ x Expected Value",
         "Age x Novelty",
         "Age x Uncertainty",
         "Age x Expected Value",
         "Novelty", 
         "Uncertainty", 
         "Expected Value")) + 
    ggtitle("Predictors of choice") +
    geom_hline(yintercept = 0, color = "grey", linetype = "dashed") +
    explo.theme
```


## Model: Influence of age, trial, value, uncertainty, and novelty on choice
```{r choice features model: age and within-block trial}
#select variables
data.model.3 <- data.model %>%
    select(c(leftChoice, evDiff, varDiff, novelDiff, age, subID, trialID)) %>%
    drop_na()

#scale continuous variables
data.model.3$evDiffScaled <- scale_this(data.model.3$evDiff)
data.model.3$varDiffScaled <- scale_this(data.model.3$varDiff)
data.model.3$novelDiffScaled <- scale_this(data.model.3$novelDiff)
data.model.3$ageScaled <- scale_this(data.model.3$age)
data.model.3$scaledTrialNum <- scale_this(data.model.3$trialID)

#run model
feature.age.trial.model = mixed(leftChoice ~ 
                                    evDiffScaled + 
                                    varDiffScaled + 
                                    novelDiffScaled +
                                    evDiffScaled:scaledTrialNum +
                                    varDiffScaled:scaledTrialNum + 
                                    novelDiffScaled:scaledTrialNum +
                                    evDiffScaled:ageScaled +
                                    varDiffScaled:ageScaled + 
                                    novelDiffScaled:ageScaled +
                                    evDiffScaled:scaledTrialNum:ageScaled +
                                    varDiffScaled:scaledTrialNum:ageScaled  + 
                                    novelDiffScaled:scaledTrialNum:ageScaled +
                                    (evDiffScaled + 
                                         varDiffScaled + 
                                         novelDiffScaled | subID),
                   data.model.3, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T)
feature.age.trial.model

summary(feature.age.trial.model)
```

```{r plot model effects: age and trial}
plot_model(feature.age.trial.model,
           type = c("est"),
           show.values = TRUE,
           show.p = TRUE,
           colors = c(color1, color2)) +
     scale_x_discrete(labels =  c(
         "Age x Novelty x Horizon",
         "Age x Uncertainty x Horizon",
         "Age x Expected Value x Horizon",
         "Age x Novelty",
         "Age x Uncertainty",
         "Age x Expected Value",
         "Novelty x Horizon",
         "Uncertainty x Horizon",
         "Expected Value x Horizon",
         "Novelty", 
         "Uncertainty", 
         "Expected Value")) + 
    ggtitle("Predictors of choice") +
    geom_hline(yintercept = 0, color = "grey", linetype = "dashed") +
    explo.theme
```

## Plot: Feature influence across trials
```{r plot horizon effects across features, fig.width=8, fig.height=5}

#compute mean choice on every trial
horizon_data <- data.model %>%
    select(ageGroup3, trialID, valuableChoice, uncertainChoice, novelChoice) %>%
    pivot_longer(cols = c(valuableChoice, uncertainChoice, novelChoice), 
                 names_to = "feature",
                 values_to = "choice") %>%
    group_by(ageGroup3, trialID, feature) %>%
    summarize(meanChoice = mean(choice, na.rm = T),
              seChoice = se(choice))

#compute rolling means for value, uncertainty, novelty
rolling_mean_choice_ev <- horizon_data %>%
    filter(feature == "valuableChoice") %>%
    group_by(ageGroup3) %>%
    summarize(rollingMeanChoice = rollmean(meanChoice, k = 3)) %>%
    mutate(feature = "valuableChoice",
                      bin = 1:n())

rolling_mean_choice_u <- horizon_data %>%
    filter(feature == "uncertainChoice") %>%
    group_by(ageGroup3) %>%
    summarize(rollingMeanChoice = rollmean(meanChoice, k = 3)) %>%
    mutate(feature = "uncertainChoice",
                      bin = 1:n())

rolling_mean_choice_n <- horizon_data %>%
    filter(feature == "novelChoice") %>%
    group_by(ageGroup3) %>%
    summarize(rollingMeanChoice = rollmean(meanChoice, k = 3)) %>%
    mutate(feature = "novelChoice",
           bin = 1:n())

rolling_mean_choices <- rbind(rolling_mean_choice_ev, rolling_mean_choice_u, rolling_mean_choice_n) 

horizon_plot <- ggplot(rolling_mean_choices, aes(x = bin, y = rollingMeanChoice, color = feature)) +
    facet_wrap(~ageGroup3) +
    geom_point() +
    geom_line() + 
    scale_color_manual(values = c(color1, color2, color3), 
                       name = "Feature",
                       labels = c("Novelty",
                                  "Uncertainty",
                                 "Expected Value")) +
    xlab("3-Trial Bin") +
    ylab("Proportion Chosen") +
    explo.theme
horizon_plot
```

## Model: Influence of trial, value, uncertainty, and novelty on choice - kids only
```{r choice features model: age and within-block trial kids only}
data.model.children <- data.model %>%
    filter(ageGroup3 == "Children") %>%
    select(leftChoice, evDiff, varDiff, novelDiff, subID, trialID) %>%
    drop_na()

#scale variables
data.model.children$evDiffScaled <- scale_this(data.model.children$evDiff)
data.model.children$varDiffScaled <- scale_this(data.model.children$varDiff)
data.model.children$novelDiffScaled <- scale_this(data.model.children$novelDiff)
data.model.children$scaledTrialNum <- scale_this(data.model.children$trialID)

#run model
feature.children.trial.model = mixed(leftChoice ~ 
                                    evDiffScaled + 
                                    varDiffScaled + 
                                    novelDiffScaled +
                                    evDiffScaled:scaledTrialNum +
                                    varDiffScaled:scaledTrialNum + 
                                    novelDiffScaled:scaledTrialNum +
                                    (evDiffScaled + varDiffScaled + novelDiffScaled || subID),
                   data.model.children, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T)
feature.children.trial.model
```


## Model: Influence of age, quadratic age, value, uncertainty, and novelty on choice
```{r choice features model: age and quadratic age}

#select variables
data.model.4 <- data.model %>%
    select(c(leftChoice, evDiff, varDiff, novelDiff, age, subID)) %>%
    drop_na()

#scale continuous variables
data.model.4$evDiffScaled <- scale_this(data.model.4$evDiff)
data.model.4$varDiffScaled <- scale_this(data.model.4$varDiff)
data.model.4$novelDiffScaled <- scale_this(data.model.4$novelDiff)
data.model.4$ageScaled <- scale_this(data.model.4$age)
data.model.4$ageSquaredScaled <- scale_this(data.model.4$age^2)

feature.quad_age.model <- mixed(leftChoice ~ 
                               evDiffScaled + 
                               varDiffScaled + 
                               novelDiffScaled +
                               evDiffScaled:ageScaled +
                               varDiffScaled:ageScaled + 
                               novelDiffScaled:ageScaled +
                               evDiffScaled:ageSquaredScaled +
                               varDiffScaled:ageSquaredScaled + 
                               novelDiffScaled:ageSquaredScaled +
                               (evDiffScaled + varDiffScaled + novelDiffScaled | subID),
                   data.model.4, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T)
feature.quad_age.model 
```

```{r plot model effects: age and quadratic age}
plot_model(feature.quad_age.model,
           type = "est",
           show.values = TRUE,
           show.p = TRUE,
           colors = c(color1, color2)) +
     scale_x_discrete(labels =  c(
         "Quadratic Age x Novelty",
         "Quadratic Age x Uncertainty",
         "Quadratic Age x Expected Value",
         "Age x Novelty",
         "Age x Uncertainty",
         "Age x Expected Value",
         "Novelty", 
         "Uncertainty", 
         "Expected Value")) + 
    ggtitle("Predictors of choice") +
    geom_hline(yintercept = 0, color = "grey", linetype = "dashed") +
    explo.theme
```


## Model: Influence of age, quadratic age, IQ, value, uncertainty, and novelty on choice
```{r choice features model: age, quadratic age, and IQ}

#select variables
data.model.5 <- data.model %>%
    select(c(leftChoice, evDiff, varDiff, novelDiff, age, subID, IQ)) %>%
    drop_na()

#scale continuous variables
data.model.5$evDiffScaled <- scale_this(data.model.5$evDiff)
data.model.5$varDiffScaled <- scale_this(data.model.5$varDiff)
data.model.5$novelDiffScaled <- scale_this(data.model.5$novelDiff)
data.model.5$ageScaled <- scale_this(data.model.5$age)
data.model.5$ageSquaredScaled <- scale_this(data.model.5$age^2)
data.model.5$IQScaled <- scale_this(data.model.5$IQ)


feature.quad_age.IQ.model = mixed(leftChoice ~ 
                                    evDiffScaled + 
                                    varDiffScaled + 
                                    novelDiffScaled +
                                    evDiffScaled:ageScaled + 
                                    varDiffScaled:ageScaled + 
                                    novelDiffScaled:ageScaled +
                                      evDiffScaled:ageSquaredScaled + 
                                    varDiffScaled:ageSquaredScaled + 
                                    novelDiffScaled:ageSquaredScaled +
                                    evDiffScaled:IQScaled +
                                    varDiffScaled:IQScaled +
                                    novelDiffScaled:IQScaled +
                                     evDiffScaled:ageScaled:IQScaled + 
                                    varDiffScaled:ageScaled:IQScaled + 
                                    novelDiffScaled:ageScaled:IQScaled +
                                      evDiffScaled:ageSquaredScaled:IQScaled + 
                                    varDiffScaled:ageSquaredScaled:IQScaled + 
                                    novelDiffScaled:ageSquaredScaled:IQScaled +
                                ((evDiffScaled + varDiffScaled + novelDiffScaled) | subID),
                   data.model.5, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T)

feature.quad_age.IQ.model

summary(feature.quad_age.IQ.model)

# main effects of EV, uncertainty, novelty
# EV x age
# EV x IQ
# marginal uncertainty x age 
# novelty x IQ
# novelty x age x IQ
# novelty x IQ x quadratic age
```

## Model: Influence of age, value, overall value (no reset), uncertainty, and novelty on choice
```{r choice features model: age, no reset value}
data.model.6  <- data.model %>%
    filter(blockID > 1) %>%
    select(c(leftChoice, evDiff, varDiff, novelDiff, age, subID, evDiff_noReset)) %>%
    drop_na()

#scale continuous variables
data.model.6$evDiffScaled <- scale_this(data.model.6$evDiff)
data.model.6$varDiffScaled <- scale_this(data.model.6$varDiff)
data.model.6$novelDiffScaled <- scale_this(data.model.6$novelDiff)
data.model.6$ageScaled <- scale_this(data.model.6$age)
data.model.6$evDiffNoResetScaled <- scale_this(data.model.6$evDiff_noReset)

#run model
feature.age.no_reset_EV.model <- mixed(leftChoice ~ 
                               evDiffScaled + 
                               varDiffScaled + 
                               novelDiffScaled +
                               evDiffNoResetScaled + 
                               evDiffScaled:ageScaled +
                               varDiffScaled:ageScaled + 
                               novelDiffScaled:ageScaled +
                               evDiffNoResetScaled:ageScaled + 
                               (evDiffScaled + varDiffScaled + novelDiffScaled + evDiffNoResetScaled || subID),
                   data.model.6, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T)
feature.age.no_reset_EV.model

#singular fit w/ correlation in RE

# main effect of EV_no_reset
# no age x EV_no_reset interaction
```

```{r model comparison evDiffNoReset vs. evDiff}
feature.age.no_reset_EV.model <- mixed(leftChoice ~ 
                               varDiffScaled + 
                               novelDiffScaled +
                               evDiffNoResetScaled + 
                               varDiffScaled:ageScaled + 
                               novelDiffScaled:ageScaled +
                               evDiffNoResetScaled:ageScaled + 
                               (varDiffScaled + novelDiffScaled + evDiffNoResetScaled || subID),
                   data.model.6, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T,
                   return = "merMod")

feature.age.EV.model <- mixed(leftChoice ~ 
                               evDiffScaled + 
                               varDiffScaled + 
                               novelDiffScaled +
                               evDiffScaled:ageScaled +
                               varDiffScaled:ageScaled + 
                               novelDiffScaled:ageScaled +
                               (evDiffScaled + varDiffScaled + novelDiffScaled || subID),
                   data.model.6, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T,
                   return = "merMod")

#both terms
feature.age.EV.no_reset_EV.model <- mixed(leftChoice ~ 
                               evDiffScaled + 
                               varDiffScaled + 
                               novelDiffScaled +
                               evDiffNoResetScaled + 
                               varDiffScaled:ageScaled + 
                               novelDiffScaled:ageScaled +
                               evDiffNoResetScaled:ageScaled + 
                               evDiffScaled:ageScaled +
                               (varDiffScaled + novelDiffScaled + evDiffNoResetScaled + evDiffScaled | subID),
                   data.model.6, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T,
                   return = "merMod")

#compare models
anova(feature.age.EV.model, feature.age.no_reset_EV.model)
# EV model fits better

anova(feature.age.EV.model, feature.age.EV.no_reset_EV.model)
# EV model fits better
```

```{r model comparison evDiffNoReset vs. evDiff children}
data.model.7 <- data.model %>%
    filter(blockID > 1) %>%
    filter(ageGroup3 == "Children") %>%
    select(c(leftChoice, evDiff, varDiff, novelDiff, subID, evDiff_noReset)) %>%
    drop_na()

#scale continuous variables
data.model.7$evDiffScaled <- scale_this(data.model.7$evDiff)
data.model.7$varDiffScaled <- scale_this(data.model.7$varDiff)
data.model.7$novelDiffScaled <- scale_this(data.model.7$novelDiff)
data.model.7$evDiffNoResetScaled <- scale_this(data.model.7$evDiff_noReset)


feature.age.no_reset_EV.model.children <- mixed(leftChoice ~ 
                               varDiffScaled + 
                               novelDiffScaled +
                               evDiffNoResetScaled + 
                               (varDiffScaled + novelDiffScaled + evDiffNoResetScaled || subID),
                   data.model.7, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T,
                   return = "merMod")

feature.age.EV.model.children <- mixed(leftChoice ~ 
                               evDiffScaled + 
                               varDiffScaled + 
                               novelDiffScaled +
                               (evDiffScaled + varDiffScaled + novelDiffScaled || subID),
                   data.model.7, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T,
                   return = "merMod")

#singular fit w/ correlated REs

#compare models
anova(feature.age.EV.model.children, feature.age.no_reset_EV.model.children)
# EV model fits better
```


```{r model comparison evDiffNoReset vs. evDiff adolescents}
data.model.7 <- data.model %>%
    filter(blockID > 1) %>%
    filter(ageGroup3 == "Adolescents") %>%
    select(c(leftChoice, evDiff, varDiff, novelDiff, subID, evDiff_noReset)) %>%
    drop_na()

#scale continuous variables
data.model.7$evDiffScaled <- scale_this(data.model.7$evDiff)
data.model.7$varDiffScaled <- scale_this(data.model.7$varDiff)
data.model.7$novelDiffScaled <- scale_this(data.model.7$novelDiff)
data.model.7$evDiffNoResetScaled <- scale_this(data.model.7$evDiff_noReset)

feature.age.no_reset_EV.model.adolescents <- mixed(leftChoice ~ 
                               varDiffScaled + 
                               novelDiffScaled +
                               evDiffNoResetScaled + 
                               (varDiffScaled + novelDiffScaled + evDiffNoResetScaled || subID),
                   data.model.7, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T,
                   return = "merMod")

feature.age.EV.model.adolescents <- mixed(leftChoice ~ 
                               evDiffScaled + 
                               varDiffScaled + 
                               novelDiffScaled +
                               (evDiffScaled + varDiffScaled + novelDiffScaled || subID),
                   data.model.7, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T,
                   return = "merMod")

#compare models
anova(feature.age.EV.model.adolescents, feature.age.no_reset_EV.model.adolescents)
# EV model fits better
```

```{r model comparison evDiffNoReset vs. evDiff adults}
data.model.7 <- data.model %>%
    filter(blockID > 1) %>%
    filter(ageGroup3 == "Adults") %>%
    select(c(leftChoice, evDiff, varDiff, novelDiff, subID, evDiff_noReset)) %>%
    drop_na()

#scale continuous variables
data.model.7$evDiffScaled <- scale_this(data.model.7$evDiff)
data.model.7$varDiffScaled <- scale_this(data.model.7$varDiff)
data.model.7$novelDiffScaled <- scale_this(data.model.7$novelDiff)
data.model.7$evDiffNoResetScaled <- scale_this(data.model.7$evDiff_noReset)


feature.age.no_reset_EV.model.adults <- mixed(leftChoice ~ 
                               varDiffScaled + 
                               novelDiffScaled +
                               evDiffNoResetScaled + 
                               (varDiffScaled + novelDiffScaled + evDiffNoResetScaled || subID),
                   data.model.7, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T,
                   return = "merMod")

feature.age.EV.model.adults <- mixed(leftChoice ~ 
                               evDiffScaled + 
                               varDiffScaled + 
                               novelDiffScaled +
                               (evDiffScaled + varDiffScaled + novelDiffScaled || subID),
                   data.model.7, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T,
                   return = "merMod")

#compare models
anova(feature.age.EV.model.adults, feature.age.no_reset_EV.model.adults)
# EV model fits better
```


## Model: Influence of value, novelty, and uncertainty of selected option on RT
```{r RT by selected option features}
#compute features of selected options
data.model <- data.model %>%
    mutate(selectedUncertainty = case_when(selectedStimID == trialStimID_1 ~ var_1,
                                           selectedStimID == trialStimID_2 ~ var_2),
           selectedValue = case_when(selectedStimID == trialStimID_1 ~ ev_1,
                                           selectedStimID == trialStimID_2 ~ ev_2),
           selectedNovelty = case_when(selectedStimID == trialStimID_1 ~ novel_1,
                                           selectedStimID == trialStimID_2 ~ novel_2))

#select relevant variables
data.model.8 <- data.model %>%
    select(c(RT, selectedUncertainty, selectedValue, selectedNovelty,
             age, subID)) %>%
    drop_na()
    

#scale continuous variables
data.model.8$selectedUncertainty <- scale_this(data.model.8$selectedUncertainty)
data.model.8$selectedValue <- scale_this(data.model.8$selectedValue)
data.model.8$selectedNovelty <- scale_this(data.model.8$selectedNovelty)
data.model.8$ageScaled <- scale_this(data.model.8$age)
data.model.8$logRT <- log(data.model$RT)


#run model
selectedUncertainty.age.model.RT <- mixed(logRT ~ 
                                    selectedUncertainty +
                                    selectedUncertainty:ageScaled +
                                    selectedValue +
                                    selectedValue:ageScaled +
                                    selectedNovelty +
                                    selectedNovelty:ageScaled +
                                        ageScaled + 
                               (selectedUncertainty + selectedValue + selectedNovelty | subID),
                   data.model.8, 
                   method = "S",
                   control = lmerControl(optimizer = "bobyqa"),
                   expand_re = T)
selectedUncertainty.age.model.RT 

# main effect of uncertainty
# main effect of value
# main effect of novelty
# age x uncertainty
# age x novelty
# no age x value
```

## Model: Influence of value, novelty, and uncertainty of selected option on RT (w/ trial number)
```{r RT by features of selected option w/ trial number}

#select data
data.model.9 <- data.model %>%
    select(c(RT, selectedUncertainty, selectedValue, selectedNovelty,
             age, subID, trialID)) %>%
    drop_na()

#scale continuous variables
data.model.9$selectedUncertainty <- scale_this(data.model.9$selectedUncertainty)
data.model.9$selectedValue <- scale_this(data.model.9$selectedValue)
data.model.9$selectedNovelty <- scale_this(data.model.9$selectedNovelty)
data.model.9$ageScaled <- scale_this(data.model.9$age)
data.model.9$trialScaled <- scale_this(data.model.9$trialID)
data.model.9$logRT <- log(data.model.9$RT)

#run model
selectedUncertainty.age.model.trial.RT <- mixed(logRT ~ 
                                    selectedUncertainty +
                                    selectedUncertainty:ageScaled +
                                    selectedValue +
                                    selectedValue:ageScaled +
                                    selectedNovelty +
                                    selectedNovelty:ageScaled +
                                        ageScaled + 
                                        trialScaled + 
                               (selectedUncertainty + selectedValue + selectedNovelty | subID),
                   data.model.9, 
                   method = "S",
                   control = lmerControl(optimizer = "bobyqa"),
                   expand_re = T)
selectedUncertainty.age.model.trial.RT 

# main effect of uncertainty
# main effect of value
# main effect of novelty
# main effect of trial
# age x uncertainty
```


## Model: Influence of value, novelty, and uncertainty of selected option on RT in children
```{r RT by features of selected option - kids only}

#select data
data.model.10 <- data.model %>%
    filter(ageGroup3 == "Children") %>%
    select(c(RT, selectedUncertainty, selectedValue, selectedNovelty,
             age, subID)) %>%
    drop_na()

#scale continuous variables
data.model.10$selectedUncertainty <- scale_this(data.model.10$selectedUncertainty)
data.model.10$selectedValue <- scale_this(data.model.10$selectedValue)
data.model.10$selectedNovelty <- scale_this(data.model.10$selectedNovelty)
data.model.10$ageScaled <- scale_this(data.model.10$age)
data.model.10$logRT <- log(data.model.10$RT)


selectedUncertainty.model.logRT.children <- mixed(logRT ~ 
                                    selectedUncertainty +
                                    selectedValue +
                                    selectedNovelty +
                                                                            selectedUncertainty:ageScaled +
                                    selectedValue:ageScaled +
                                    selectedNovelty:ageScaled +
                                        ageScaled +
                               (selectedUncertainty + selectedValue + selectedNovelty || subID),
                   data.model.10, 
                   method = "S",
                   control = lmerControl(optimizer = "bobyqa"),
                   expand_re = T)
selectedUncertainty.model.logRT.children 

# main effects of:
# uncertainty
# value
# novelty
```

## Model: Influence of value, novelty, and uncertainty of selected option on RT in children w/ trial number
```{r RT by features of selected option - kids only with trial number}
#select data
data.model.11 <- data.model %>%
    filter(ageGroup3 == "Children") %>%
    select(c(RT, selectedUncertainty, selectedValue, selectedNovelty,
             age, subID, trialID)) %>%
    drop_na()

#scale continuous variables
data.model.11$selectedUncertainty <- scale_this(data.model.11$selectedUncertainty)
data.model.11$selectedValue <- scale_this(data.model.11$selectedValue)
data.model.11$selectedNovelty <- scale_this(data.model.11$selectedNovelty)
data.model.11$ageScaled <- scale_this(data.model.11$age)
data.model.11$trialScaled <- scale_this(data.model.11$trialID)
data.model.11$logRT <- log(data.model.11$RT)

#run model
selectedUncertainty.model.logRT.trial.children <- mixed(logRT ~ 
                                    selectedUncertainty +
                                    selectedValue +
                                    selectedNovelty +
                                        selectedUncertainty:ageScaled +
                                        selectedValue:ageScaled +
                                        selectedNovelty:ageScaled +
                                        ageScaled +
                                        trialScaled + 
                               (selectedUncertainty + selectedValue + selectedNovelty || subID),
                   data.model.11, 
                   method = "S",
                   control = lmerControl(optimizer = "bobyqa"),
                   expand_re = T)
selectedUncertainty.model.logRT.trial.children 

# main effects of:
# uncertainty
# novelty
# trial 
```

## Plot: RT Model effects
```{r rt model effects plot}
selectedUncertainty.model.logRT.merMod <- mixed(logRT ~ 
                                    selectedUncertainty +
                                    selectedUncertainty:ageScaled +
                                    selectedValue +
                                    selectedValue:ageScaled +
                                    selectedNovelty +
                                    selectedNovelty:ageScaled +
                                        ageScaled + 
                               (selectedUncertainty + selectedValue + selectedNovelty || subID),
                   data.model.10,
                   method = "S",
                   control = lmerControl(optimizer = "bobyqa"),
                   expand_re = T,
                   return = "merMod")

rt_model_plot <- plot_model(selectedUncertainty.model.logRT.merMod, 
           type = "int",
           mdrt.values = "meansd") 
rt_model_plot
```

## Plot: RT by uncertainty of selected option and age
```{r rt by selected uncertainty and age, fig.height=4, fig.width=5}
data.model$logRT <- log(data.model$RT)

rt_selectedUncertainty_plot <- ggplot(data.model, aes(x = selectedUncertainty, y = logRT, color = ageGroup3, fill = ageGroup3)) +
    geom_point(size = .1, alpha = .1) +
    geom_smooth(method = "lm") +
    scale_color_manual(values = c(color1, color2, color3), name = "Age Group") +
    scale_fill_manual(values = c(color1, color2, color3), name = "Age Group") +
    xlab("Uncertainty of Selected Option") +
    ylab("Log RT") +
    explo.theme
rt_selectedUncertainty_plot
```

## Plot: RT by value of selected option and age
```{r rt by selected value and age, fig.height=4, fig.width=5}

rt_selectedValue_plot <- ggplot(data.model, aes(x = selectedValue, y = logRT, color = ageGroup3, fill = ageGroup3)) +
    geom_point(size = .1, alpha = .1) +
    geom_smooth(method = "lm") +
    scale_color_manual(values = c(color1, color2, color3), name = "Age Group") +
    scale_fill_manual(values = c(color1, color2, color3), name = "Age Group") +
    xlab("Expected Value of Selected Option") +
    ylab("Log RT") +
    explo.theme
rt_selectedValue_plot
```

## Plot: RT by novelty of selected option and age
```{r rt by selected novelty and age, fig.height=4, fig.width=5}

rt_selectedNovelty_plot <- ggplot(data.model, aes(x = selectedNovelty, y = logRT, color = ageGroup3, fill = ageGroup3)) +
    geom_point(size = .1, alpha = .1) +
    geom_smooth(method = "lm") +
    scale_color_manual(values = c(color1, color2, color3), name = "Age Group") +
    scale_fill_manual(values = c(color1, color2, color3), name = "Age Group") +
    xlab("Novelty of Selected Option") +
    ylab("Log RT") +
    explo.theme
rt_selectedNovelty_plot
```

## Plot: Binned feature values vs. RT
```{r binned feature value plot, eval = F}
temp <- data.model %>%
    mutate(uncertaintyBin = cut(selectedUncertainty, 10),
           valueBin = cut(selectedValue, 10),
           noveltyBin = cut(selectedNovelty, 10)) 

uncertaintyRTMeans <- temp %>%
    group_by(uncertaintyBin, ageGroup3) %>%
    summarize(meanLogRT = mean(logRT, na.rm = T),
              seLogRT = se(logRT))

valueRTMeans <- temp %>%
    group_by(valueBin, ageGroup3) %>%
    summarize(meanLogRT = mean(logRT, na.rm = T),
              seLogRT = se(logRT))

noveltyRTMeans <- temp %>%
    group_by(noveltyBin, ageGroup3) %>%
    summarize(meanLogRT = mean(logRT, na.rm = T),
              seLogRT = se(logRT))

#Uncertainty
ggplot(uncertaintyRTMeans, aes(x = uncertaintyBin, y = meanLogRT, color = ageGroup3)) +
    geom_point() +
    geom_line(aes(group = ageGroup3)) +
    geom_errorbar(aes(ymin = meanLogRT - seLogRT, ymax = meanLogRT + seLogRT), width = .1) +
    scale_color_manual(values = c(color1, color2, color3), name = "Age Group") +
    xlab("uncertainty") +
    ylab("Mean Log RT") +
    explo.theme

#Novelty
ggplot(noveltyRTMeans, aes(x = noveltyBin, y = meanLogRT, color = ageGroup3)) +
    geom_point() +
    geom_line(aes(group = ageGroup3)) +
    geom_errorbar(aes(ymin = meanLogRT - seLogRT, ymax = meanLogRT + seLogRT), width = .1) +
    scale_color_manual(values = c(color1, color2, color3), name = "Age Group") +
    xlab("Novelty") +
    ylab("Mean Log RT") +
    explo.theme


#Value
ggplot(valueRTMeans, aes(x = valueBin, y = meanLogRT, color = ageGroup3)) +
    geom_point() +
    geom_line(aes(group = ageGroup3)) +
    geom_errorbar(aes(ymin = meanLogRT - seLogRT, ymax = meanLogRT + seLogRT), width = .1) +
    scale_color_manual(values = c(color1, color2, color3), name = "Age Group") +
    xlab("Expected Value") +
    ylab("Mean Log RT") +
    explo.theme

```


## Do individual differences in uncertainty aversion relate to individual differences in effects of uncertainty on RT?
```{r uncertainty aversion RT relation}

data.model.12 <- data.model %>%
    select(c(leftChoice, RT, selectedUncertainty, selectedValue, selectedNovelty, 
             evDiff, varDiff, novelDiff, subID)) %>%
    drop_na()

#scale continuous variables
data.model.12$selectedUncertainty <- scale_this(data.model.12$selectedUncertainty)
data.model.12$selectedValue <- scale_this(data.model.12$selectedValue)
data.model.12$selectedNovelty <- scale_this(data.model.12$selectedNovelty)
data.model.12$evDiffScaled <- scale_this(data.model.12$evDiff)
data.model.12$varDiffScaled <- scale_this(data.model.12$varDiff)
data.model.12$novelDiffScaled <- scale_this(data.model.12$novelDiff)
data.model.12$logRT <- log(data.model.12$RT)


#first, extract uncertainty slope from choice model (w/o age)
feature.choice.merMod <- mixed(leftChoice ~ 
                               evDiffScaled + 
                               varDiffScaled + 
                               novelDiffScaled +
                               (evDiffScaled + varDiffScaled + novelDiffScaled | subID),
                   data.model.12, 
                   family = binomial, 
                   method = "LRT",
                   control = glmerControl(optimizer = "bobyqa"),
                   expand_re = T, 
                   return = "merMod")

choiceUncertaintySlope <- ranef(feature.choice.merMod)$subID$re1.varDiffScaled
subID <- rownames(ranef(feature.choice.merMod)$subID)
choiceREs <- data.frame(subID, choiceUncertaintySlope)


#then, extract uncertainty slope from RT model (w/o age)
selectedUncertainty.logRT.merMod <- mixed(logRT ~ 
                                    selectedUncertainty +
                                    selectedValue +
                                    selectedNovelty +
                               (selectedUncertainty + selectedValue + selectedNovelty | subID),
                   data.model.12, 
                   method = "S",
                   control = lmerControl(optimizer = "bobyqa"),
                   expand_re = T,
                   return = "merMod")

RTUncertaintySlope <- ranef(selectedUncertainty.logRT.merMod)$subID$re1.selectedUncertainty
subID <- rownames(ranef(selectedUncertainty.logRT.merMod)$subID)
RTREs <- data.frame(subID, RTUncertaintySlope)

#combine
temp <- full_join(choiceREs, RTREs, by = c("subID")) 
temp$subID <- as.numeric(temp$subID)

#add age
uncertaintyREs <- demographicData %>%
    select(subID, age, ageGroup3) %>%
    right_join(temp, by = c("subID"))

#scale
uncertaintyREs$ageScaled <- scale_this(uncertaintyREs$age)
uncertaintyREs$choiceSlopeScaled <- scale_this(uncertaintyREs$choiceUncertaintySlope)
uncertaintyREs$RTSlopeScaled <- scale_this(uncertaintyREs$RTUncertaintySlope)

#run regression
uncertaintyRelation.lm <- lm(choiceSlopeScaled ~ ageScaled * RTSlopeScaled, data = uncertaintyREs)
pander(uncertaintyRelation.lm)
```

## Plot: Do individual differences in uncertainty aversion relate to individual differences in effects of uncertainty on RT?
```{r uncertainty relation plot}
uncertaintyRelation_plot <- ggplot(uncertaintyREs, aes(x = RTUncertaintySlope, y = choiceUncertaintySlope)) +
    geom_point(color = color2, size = 1, alpha = 1) +
    geom_smooth(method = "lm", color = color1, fill = color1) +
    xlab("Uncertainty Random Effect (RT)") +
    ylab("Uncertainty Random Effect (Choice)") +
    explo.theme
uncertaintyRelation_plot
```


# Memory Test
```{r process memory data}
#import mem Data
memData <- read_csv(file.path(dataDir, "explo_mem_data.csv"))

# get sub ages
ageData <- demographicData %>%
    select(subID, age, ageGroup3, ageGroup4, IQ)

#combine with demographic data
memData <- inner_join(memData, ageData, by = c("subID"))

#determine response made and compute accuracy
memData <- memData %>%
    mutate(resp = case_when(respKey == 1 ~ imageOrder_1,
                            respKey == 2 ~ imageOrder_2,
                            respKey == 3 ~ imageOrder_3, 
                            respKey == 4 ~ imageOrder_4, 
                            respKey == 5 ~ imageOrder_5),
           mem_resp = case_when(resp == 1 ~ "High",
                                resp == 2 ~ "Low",
                                resp == 3 ~ "Med",
                                resp == 4 ~ "High_Diff",
                                resp == 5 ~ "Foil"),
           mem_acc = case_when(resp == 1 ~ 1,
                               resp != 1 ~ 0))

memData$mem_resp <- factor(memData$mem_resp, levels = c("High", "Med", "Low", "High_Diff", "Foil"))

```

## Model: Memory accuracy vs. chance performance
```{r memory accuracy vs chance}
sub_mem_acc <- memData %>%
    group_by(subID) %>%
    summarize(mean_mem_acc = mean(mem_acc, na.rm = T))

mem_acc.ttest <- t.test(sub_mem_acc$mean_mem_acc, mu = .2)
mem_acc.ttest

group_mem_acc <- sub_mem_acc %>%
    summarize(group_mean_mem_acc = mean(mean_mem_acc),
              mem_se = se(mean_mem_acc))
group_mem_acc
```

## Model: Memory accuracy by age 
```{r memory accuracy by age model}
memData$ageScaled <- scale_this(memData$age)

mem.age.model <- glm(mem_acc ~ ageScaled, family = "binomial", data = memData)
pander(summary(mem.age.model))

#no effect of age on memory accuracy
```


## Plot: Memory accuracy by age
```{r mean memory accuracy by age}
meanMemData <- memData %>%
    group_by(subID, age) %>%
    summarize(meanMemAcc = mean(mem_acc, na.rm = T))

meanMemPlot <- ggplot(meanMemData, aes(x = age, y = meanMemAcc)) +
    geom_point(color = color1) + 
    geom_smooth(method = "lm", color = color2, fill = color2) +
    ylab("Mean Memory Accuracy") +
    xlab("Age") +
    explo.theme
meanMemPlot
```

## Stats: Mean memory accuracy by age group
```{r mean memory accuracy by age group}
meanMemData <- memData %>%
    group_by(ageGroup3) %>%
    summarize(meanMemAcc = mean(mem_acc, na.rm = T))
```

## Plot: Distribution of memory responses
```{r mem plot response distribution}

#compute each subject's distribution of responses
memRespSubCounts <- memData %>%
    group_by(subID, age, ageGroup3, mem_resp) %>%
    drop_na() %>%
    summarize(N = n()) %>%
    ungroup() %>%
    group_by(subID) %>%
    mutate(prop = N / sum(N))

memRespCounts <- memRespSubCounts %>%
    group_by(ageGroup3, mem_resp) %>%
    summarize(meanProp = mean(prop, na.rm = T),
              seProp = se(prop))

#plot
memRespPlot <- ggplot(memRespCounts, aes(x = mem_resp, fill = ageGroup3, y = meanProp)) +
    geom_bar(stat = "identity", position = "dodge", color = "black") +
    geom_errorbar(aes(ymin = meanProp - seProp, ymax = meanProp + seProp), width = .1, position = position_dodge(width = .9)) +
    #facet_wrap(~ageGroup) +
    scale_fill_manual(values = c(color1, color2, color3), name = "Age Group") + 
    xlab("Response") +
    ylab("Proportion of Responses") +
    scale_x_discrete(labels = c("High Reward", "Med Reward", "Low Reward", "High Different", "New")) +
    geom_hline(yintercept = .2, linetype = "dashed") +
    explo.theme +
    theme(legend.position = "top", 
          axis.text.x = element_text(angle = 75, vjust = .5))
memRespPlot
```


# Model comparison
```{r pxps}
pxps <- read_csv(file.path(dataDir, "model_output/pxps.csv"), col_names = F) %>%
    rownames_to_column() %>%
    mutate(ageGroup = case_when(rowname == 1 ~ "Children",
                                rowname == 2 ~ "Adolescents",
                                rowname == 3 ~ "Adults")) %>%
    select(-rowname) %>%
    pivot_longer(cols = X1:X6,
                 values_to = "value",
                 names_to = "model")%>%
    mutate(value_type = "Protected Exceedance Probability")

freq <-read_csv(file.path(dataDir, "model_output/model_freq.csv"), col_names = F) %>%
    rownames_to_column() %>%
    mutate(ageGroup = case_when(rowname == 1 ~ "Children",
                                rowname == 2 ~ "Adolescents",
                                rowname == 3 ~ "Adults")) %>%
    select(-rowname) %>%
    pivot_longer(cols = X1:X6,
                 values_to = "value",
                 names_to = "model")%>%
    mutate(value_type = "Model Frequency")

model_stats <- rbind(pxps, freq) %>%
    filter(model %in% c("X2", "X3", "X5"))

model_stats$ageGroup <- factor(model_stats$ageGroup, levels = c("Children", "Adolescents", "Adults"))
```

```{r plot model stats}

model_stats_plot <- ggplot(model_stats, aes(x = ageGroup, fill = model, y = value)) +
    facet_wrap(~value_type, ncol = 1) +
    geom_bar(stat = "identity", position = "dodge", color = "black") + 
    scale_fill_manual(values = c(color1, color2, color3),
                      name = "Model",
                      labels = c("Novelty bias",
                                 "Novelty + uncertainty bias",
                                 "Familiarity-gated uncertainty")) +
    xlab("Age Group") +
    ylab("Value") +
    explo.theme
model_stats_plot
```